{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-24 documents/background.tex
Writing

@@

>>>>

\begin{autem}

{\Large {This has \textbf{nothing to do} with 5G communications. }}\\

I am comfortable making such a definitive statement.

The power levels required to even begin to observe this inactivation effect in practice are so high that, if conditions are not specifically tailored for clinical use, extensive burns will result within seconds. Even in this case, the effect is to eviscerate the virus, not to aid its spread.

Moreover, these frequency bands have been in almost continuous use not long after Jagadish Chandra Bose 1894; the world has been bathed in high-power 10 GHz pulses at least since the commissioning of the first centimeter-wave weather radars in 1959.

Countless far more prosaic explanations exist in the modern world, such as air travel.

If you have any concerns regarding this statement, please contact me. I would be happy to discuss this.

\end{autem}

@@

In fact, it seems like at some point in the 1970, a selective effect on viruses was discovered and progressed as far as a clinical trial. The only record we have of this trial are two citations regarding a conference paper submitted to a New York Academy of Sciences symposium in a 1981 index. This symposium is not listed in Transactions of. The National Institutes of Health may have a copy.

### 2020-11-24 documents/detection.tex
Writing

\begin{autem}
	I hasten to note that quantifying phage titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent here was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the small volume constraints of our original poorly designed microwave setup.
\end{autem}

@@

As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile. One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.

>>>>

\begin{autem}
	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent here was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the small volume constraints of our original poorly designed microwave setup.
\end{autem}

@@

As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile. One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters. Probably Syringe filters are a good alternative.

### 2020-11-24 documents/lessons_learned.tex
nah.
Writing

>>>>

Indexes of papers compiled by government agencies, and gray literature in general, appear to be very useful.

Rigorous literature reviews are very important. de Seze has a good example: search terms are specified. If we had come across the paper by Bigior earlier, we may have

Papers only carry the scientific heritage that their authors saw fit to include in the references section.

### 2020-11-24 documents/pseudo_soliton.tex
Writing

\begin{sidenote}
There are some extremely tricky subtleties in the simulation.  \cite{propagation1992}. In \cite{Comments1993}, Leubbers says FDTD and FFT both are better than Asympt, Ogh says no there's no problem, Asymptotic is really accurate. Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.
\end{sidenote}

As saliently noted by Adair:

\begin{quote}
	“the energy of the pulse at a depth of 1 cm is about 0.8% of the initial energy;
	the maximum electric field strength, E is reduced by a factor of about 12, and the maximum rate-ofchange of the field, dE/dt, is reduced by a factor of 20. Every characteristic of the pulse at depth is
	contained, albeit attenuated, in the initial pulse. Consequently, we do not find it credible that the
	strongly attenuated pulse – albeit with a different shape – can induce biological effects beyond that of
	the initial pulse.”
\end{quote}

>>>>

The prototypical Vircator (not varactor) pinched electron beam tubes

step recovery diodes

\begin{sidenote}
There are some extremely tricky subtleties in the simulation.  \cite{propagation1992}. In \cite{Comments1993}, Leubbers says FDTD and FFT both are better than Asympt, Ogh says no there's no problem, Asymptotic is really accurate. Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.
\end{sidenote}
\begin{tab}
	content
\end{tab}
